Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition.

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
typos, commas

There is some previous work applying BERT to dialogue.
\citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
Similarly \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
\citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora. In our work we are not attempting to beat the current state-of-the-art due to the different aims of the study.

@@

To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as a the sequence model, but the accuracy was not significantly different compared to RNN. It can be explained by the absence of longer distance dependencies on this level of our model.} 
The RNN takes the encoded utterance as input at each time step,
and its hidden state is passed to a simple linear classification layer over dialogue act tags.
Conceptually, the encoded utterance represents the context-agnostic features of the utterance, and the hidden state of the RNN represents the full discourse context.

@@

Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought. Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix. However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
Importantly, laughter helps to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
\begin{table}
      \small
  \centering
  \begin{tabularx}{\linewidth}{llL}
    \toprule
    Speaker & DA & Utterance \\ \midrule
        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
    B   & sd	&  Um, as far as spare time, they talked about, \\
    B	& \% & I don't, + I think, \\
    B	& qh & who has any spare time \texttt{<laughter>}? \\
    A	& x & \texttt{<laughter>}.\\
             \bottomrule
  \end{tabularx}
  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
  \label{table:example-qh}
\end{table}

@@

Next, we assess the effect of additional dialogue pre-training on BERT's performance as an utterance encoder.\footnote{
In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
\citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
We want to see if BERT can bennefit from pre-training, on dialogue data, including from data outside the immediate target domain.

>>>>

There is some previous work applying BERT to dialogue.
\citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
Similarly, \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
\citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora. In our work we are not attempting to beat the current state-of-the-art due to the different aims of the study.

@@

To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN. It can be explained by the absence of longer distance dependencies on this level of our model.} 
The RNN takes the encoded utterance as input at each time step,
and its hidden state is passed to a simple linear classification layer over dialogue act tags.
Conceptually, the encoded utterance represents the context-agnostic features of the utterance, and the hidden state of the RNN represents the full discourse context.

@@

Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought. Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix. However, there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
Importantly, laughter helps to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
Therefore, questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
\begin{table}
      \small
  \centering
  \begin{tabularx}{\linewidth}{llL}
    \toprule
    Speaker & DA & Utterance \\ \midrule
        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
    B   & sd	&  Um, as far as spare time, they talked about, \\
    B	& \% & I don't, + I think, \\
    B	& qh & who has any spare time \texttt{<laughter>}? \\
    A	& x & \texttt{<laughter>}.\\
             \bottomrule
  \end{tabularx}
  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
  \label{table:example-qh}
\end{table}

@@

Next, we assess the effect of additional dialogue pre-training on BERT's performance as an utterance encoder.\footnote{
In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
\citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
We want to see if BERT can benefit from pre-training, on dialogue data, including from data outside the immediate target domain.
